Supermassive black holes and their host spheroids \\ II. The red and blue sequence in the $M_{\rm BH} - M_{\rm *,sph}$ diagram

### 2015-11-20 papers/MbhMsph/mm.tex
the victory day

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

@@

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
and define a tight %\emph{early-type sequence} 
\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper %\emph{late-type sequence}, 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

%It should also be noted that $\sim$80\% of their core-S\'ersic spheroids were morphologically classified as elliptical galaxies, 
%and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
%Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
%such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
%However, \cite{grahamscott2013} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
%are not randomly offset from such near-linear correlation, 
%but follow the steeper relation traced by the S\'ersic spheroids. 
%Using bulge/disk decomposition data from \cite{jiang2011a}, 
%\cite{grahamscott2015} derived the host spheroid masses 
%and showed that the steeper $M_{\rm BH} - M_{\rm *,sph}$ extends to these spheroids with even lower black hole masses 
%($10^{5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 2 \times 10^{6}$), 
%and a more detailed analysis will be presented in Graham et al. (2015, \emph{in preparation}).  \\
Here we investigate in more detail %substructure in 

@@

%{\bf This paper is structured as follows... }

@@

%to investigate the $M_{\rm BH} - L_{\rm gal}$, $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 

@@

Most of these factors are not included in popular 2D fitting codes which report only the {\bf statistical} errors associated with their fitted parameters. 

@@

{\bf Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters.} } 

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}) data,
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis using both the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All of these three linear regression routines account for the intrinsic scatter, 
but only the last two allow one to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic and for early/late-type galaxies.
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical forward ($M_{\rm BH}|X$) regressions -- 
which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
are best used to predict black hole masses.

@@

%Late-type (Sp) (13) & BCES $(Y|X)$      & $7.37 \pm 0.17$ & $-0.33 \pm 0.87$   & $-24.39$ & $-$ & $0.65$ \\
%                    & BCES $(X|Y)$      & $7.37 \pm 1.97$ & $-21.66 \pm 53.74$ & $-24.39$ & $-$ & $7.73$ \\
%                    & BCES Bisector     & $7.37 \pm 0.20$ & $-1.32 \pm 0.94$   & $-24.39$ & $-$ & $0.77$ \\
%                    & FITEXY $(Y|X)$    & $7.38^{+0.17}_{-0.18}$ & $-0.34^{+0.74}_{-0.80}$ & $-24.39$ & $0.63^{+0.19}_{-0.11}$ & $0.65$ \\
%                    & FITEXY $(X|Y)$    & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & FITEXY Bisector   & $$ & $$ & $-24.39$ & $-$    & $$ \\
%                    & {\tt linmix\_err} $(Y|X)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} $(X|Y)$     & $$ & $$ & $-24.39$ & $$ & $$ \\
%                    & {\tt linmix\_err} Bisector    & $$ & $$ & $-24.39$ & $-$    & $$ \\

%All (62)               & BCES $(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES $(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%                       & FITEXY $(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY $(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
%                       & {\tt linmix\_err} $(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & {\tt linmix\_err} $(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & {\tt linmix\_err} Bisector    & $$ & $$ & $$ & $-$    & $$ \\

@@

The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. \\

@@

That is, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

@@

%Ellipticals (E) (30)   & BCES $(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
%                      & BCES $(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
%                      & FITEXY $(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
%                      & FITEXY $(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES $(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
%                      & BCES $(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
%                      & FITEXY $(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
%                      & FITEXY $(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario\footnote{\bf In dry mergers, the black hole and the bulge grow at the same pace, 
increasing their mass in lock step.},
and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
\cite{graham2012bent} reported that the $M_{\rm BH}/M_{\rm dyn,sph}$ ratio for core-S\'ersic galaxies was 0.36\% 
($M_{\rm dyn,sph}$ is the spheroid dynamical mass), 
and discussed the many implications of this.  
Using a larger data sample, \cite{grahamscott2013} reported that the $M_{\rm BH}/M_{\rm *,sph}$ ratio was 0.49\% for core-S\'ersic galaxies.   
Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
boosts estimates of the black hole mass function and mass density based on galaxy/spheroid luminosity functions. \\
The bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
whose slope is less well constrained due to the smaller size of the subsample and, more importantly, 
to the smaller range in $M_{\rm *,sph}$ that the subsample spans. 
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with a slope $= 3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $= 2.28^{+1.67}_{-1.01}$.
%The Bayesian estimator of \cite{linmixerr} fails in performing an inverse $(X|Y)$ linear regression for the subsample of spiral galaxies. 
More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
with the current technological resources. 
In this regard, using a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with virial
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a}, 
\cite{grahamscott2015} showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges.
The majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(NASA Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.} and
we anticipate here that the correlation traced by our spiral galaxy bulges 
may track the location of these lower mass AGN in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
and this will be explored with more rigour in a forthcoming paper.

@@

      %For analogy with the color-magnitude diagram, 
      %it may be tempting to refer to our \emph{early-type sequence} as a \emph{red sequence} 
      %and to our \emph{late-type sequence} as a \emph{blue sequence}.
      %Future work will explore the color of spheroids and galaxies in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.  

@@

\item Spheroids with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. 

@@

      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ {\bf (see also \citealt{erwingadotti2012,beifiori2012})}. 

@@

\acknowledgments
GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. \\
% referee thank you!!
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.

>>>>

@@

\begin{abstract}
In our first paper, we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}.
Our sample is the largest to date and, for the first time, the decompositions were checked for consistency with the galaxy kinematics. 
We present correlations between the black hole mass, $M_{\rm BH}$, 
and the host spheroid (and galaxy) luminosity, $L_{\rm sph}$ (and $L_{\rm gal}$), 
and also stellar mass, $M_{\rm *,sph}$.
Most previous studies have used galaxy samples that were overwhelmingly dominated by high-mass, early-type galaxies.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to better investigate the poorly studied low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ correlation.
The bulges of early-type (E + S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$  
and define a tight 
\emph{red sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ 
and a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.68 \pm 0.04\%$, 
i.e.~a $\pm 2\sigma$ range of 0.1--5\%.
At the low-mass end, the bulges of late-type (Sp) galaxies define a much steeper 
\emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{2-3}$, 
indicating that gas-rich processes feed the black hole more efficiently than the host bulge as they coevolve. 
We additionally report that: i) S\'ersic galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.48 \pm 0.20}$, a less steep sequence than previously reported; 
ii) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by the current bulge sample with $n_{\rm sph}>2$; 
and iii) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies 
(most elliptical galaxies contain disks, i.e.~$L_{\rm sph} \neq L_{\rm gal}$) --
once reasonable numbers of spiral galaxies are included, the correlation with $L_{\rm sph}$ is better than that with $L_{\rm gal}$.

@@

Here we investigate in more detail 

@@

@@

@@

Most of these factors are not included in popular 2D fitting codes which report only the statistical errors associated with their fitted parameters. 

@@

Unlike many papers, we believe that we have not under-estimated the uncertainties associated to the bulge best-fit parameters. } 

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm gal}$ (see Table \ref{tab:lreggal}), 
$M_{\rm BH} - L_{\rm sph}$ (see Table \ref{tab:lregsph}) and $M_{\rm BH} - M_{\rm *,sph}$ (see Table \ref{tab:lregmass}) data,
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis using both the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
All of these three linear regression routines account for the intrinsic scatter, 
but only the last two allow one to quantify it.
We report linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic and for early/late-type galaxies.
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical forward ($M_{\rm BH}|X$) regressions -- 
which minimize the scatter in the $\log(M_{\rm BH})$ direction -- 
are best used to predict black hole masses.

@@

@@

The use of the S\'ersic index (in addition to rotation) to identify pseudo-bulges is thus a dangerous practice. 
{\bf We therefore do not assume that all bulges with $n_{\rm sph}<2$ are built from internal processes in the disk 
(i.e.~are what some authors call pseudo-bulges). } \\

@@

That is, within the current dataset, 
bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$. \\

@@

@@

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
and its linear regression analysis in Table \ref{tab:lregmass}. 
The bulges of the early-type galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.04 \pm 0.10}$,
consistent with a dry-merging formation scenario\footnote{In dry mergers, the black hole and the bulge grow at the same pace, 
increasing their mass in lock step.},
and define a tight \emph{early-type sequence} with intrinsic scatter $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$. 
\cite{graham2012bent} reported that the $M_{\rm BH}/M_{\rm dyn,sph}$ ratio for core-S\'ersic galaxies was 0.36\% 
($M_{\rm dyn,sph}$ is the spheroid dynamical mass), 
and discussed the many implications of this.  
Using a larger data sample, \cite{grahamscott2013} reported that the $M_{\rm BH}/M_{\rm *,sph}$ ratio was 0.49\% for core-S\'ersic galaxies.   
Here we find a median $M_{\rm BH}/M_{\rm *,sph}$ ratio of $0.50 \pm 0.04\%$ for the 22 core-S\'ersic galaxies 
and $0.68 \pm 0.04\%$ for the 45 early-type galaxies.  
Among other things, this higher value (previously reported to be $0.1 - 0.2\%$ for all galaxy types, e.g.~\citealt{marconihunt2003}), 
boosts estimates of the black hole mass function and mass density based on galaxy/spheroid luminosity functions. \\
The bulges of the spiral galaxies trace a steeper \emph{late-type sequence}, 
whose slope is less well constrained due to the smaller size of the subsample and, more importantly, 
to the smaller range in $M_{\rm *,sph}$ that the subsample spans. 
For the bulges of spiral galaxies, the BCES code returns a log-linear relation with a slope $= 3.00 \pm 1.30$, 
while the modified FITEXY routine finds a shallower (but still consistent within the $1\sigma$ uncertainty) 
slope $= 2.28^{+1.67}_{-1.01}$.
More data would be welcome to better constrain the slope of this \emph{late-type sequence}, 
although we note that direct measurements of black hole masses below $10^6\rm~M_\odot$ are extremely challenging to obtain 
with the current technological resources. 
In this regard, using a sample of $\sim$140 low-redshift ($z \leq 0.35$, with a median redshift $\langle z \rangle = 0.085$) 
bulges hosting Active Galactic Nuclei (AGNs) with virial
black hole masses $10^5 \lesssim M_{\rm BH}/{\rm M_\odot} \lesssim 2 \times 10^6$ \citep{jiang2011a}, 
\cite{grahamscott2015} showed that they roughly follow the quadratic $M_{\rm BH} - M_{\rm *,sph}$ relation defined by their S\'ersic bulges.
The majority of our spiral galaxies host an AGN\footnote{According to the nuclear classification reported on NED 
(NASA Extragalactic Database), among our 17 spiral galaxies, at least 12 host a Seyfert AGN and one hosts a LINER AGN.} and
we anticipate here that the correlation traced by our spiral galaxy bulges 
may track the location of these lower mass AGN in the $M_{\rm BH} - M_{\rm *,sph}$ diagram.
That is, the AGNs appear to be the low-mass continuation of our tentative \emph{late-type sequence} shown in Figure \ref{fig:mbhmasssph} 
and this will be explored with more rigour in a forthcoming paper. \\

{\bf 
As a final remark, we comment on the work done by \cite{reinesvolonteri2015}, 
who investigated the relationship between black hole mass and total galaxy stellar mass, $M_{\rm *,gal}$. 
Their Figure 8 presents the $M_{\rm BH} - M_{\rm *,gal}$ distribution 
for a sample of $\approx 260$ local AGNs with virial black hole masses  
and for $\approx 80$ galaxies with dynamical black hole masses. 
They concluded that the AGN sample and the early-type galaxies with quiescent black holes define two distinct sequences 
in their $M_{\rm BH} - M_{\rm *,gal}$ diagram; 
these two sequences have similar slope, but a normalization factor different by more than one order of magnitude.  
Since we noted that the \cite{jiang2011a} AGN sample follows the steeper $M_{\rm BH} - M_{\rm *,sph}$ correlation 
traced by our spiral galaxy bulges (the majority of which host an AGN), 
it would be interesting to recover the $M_{\rm BH} - M_{\rm *,sph}$ distribution 
also for the AGN sample of \cite{reinesvolonteri2015}. \\
However we do note that there is emerging evidence (e.g.~\citealt{busch2015,subramanian2015}) 
for a population of bulges with black hole masses residing below (or to the right of) the red and blue $M_{\rm BH} - M_{\rm *,sph}$ 
sequences constructed here using samples with directly measured black hole masses, as speculated by Batcheldor (2010).
}

@@

@@

\item {\bf It has been argued that pseuso-bulges (disk-like, rotation-supported systems, built from secular processes) 
      do not follow the $M_{\rm BH} - L_{\rm sph}$ correlation defined by classical bulges 
      (spheroidal, pressure-supported systems, formed through violent processes).  
      The recent literature (e.g.~\citealt{sani2011,beifiori2012}) has distinguished between pseudo- and classical bulges 
      according to their S\'ersic index, $n_{\rm sph}$. 
      Although we do not consider the S\'ersic index a good indicator as of the nature of a bulge (e.g.~\citealt{grahamworley2008}), 
      we investigated this point and found that, within the current dataset,  
      spheroids with $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
      are not offset to lower $M_{\rm BH}$ from the $M_{\rm BH} - L_{\rm sph}$ correlation defined by spheroids with $n_{\rm sph}>2$. }

@@

      $M_{\rm BH}$ correlates better with $L_{\rm sph}$ than with $L_{\rm gal}$ (see also \citealt{erwingadotti2012,beifiori2012}). 

@@

\acknowledgments
GS warmly thanks Luca Cortese, Elisabete Lima Da Cunha, Duncan Forbes and Gonzalo Diaz for useful discussion. 
We also thank the anonymous referee for useful comments and suggestions. 
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
